\Large \bf Redstone: a Modular Deterministic Simulation Testing Framework for Distributed Systems

### 2024-06-07 paper/paper.tex
Shakespearized first two sections

%-------------------------------------------------------------------------------
\begin{abstract}
%-------------------------------------------------------------------------------
{\fontsize{12}{15}\selectfont 
In testing distributed systems,
confirming a system's tolerance of faults in disks and networks is not only useful but necessary.
Redstone, a modular deterministic simulation testing framework,
amplifies failures in various substrates underlying a distributed system
in order to confirm the system's ability to withstand these failures.
We intercept calls to the kernel for the disk and the network, as well as to clock functions,
introducing our own code.
Determinism allows reproduction of failure conditions,
allowing developers to confirm, having encountered and debugged a failure,
that their system will not fail again when confronted by identical conditions.
Our control over clock functions further allows us to "accelerate" time,
increasing ability to test faster, and to emulate the effects of clock jitter.
Finally, because Redstone is inherently modular,
it is simple to extend and port to a wider variety of applications and platforms.
}
\end{abstract}

@@

"Consistently" is another key phrase here,
as a test must be replicable.
% just running the system a few times doesn't confirm that everything that can go wrong has gone wrong.
As such,
a good testing system must not only introduce failures,
but be able to repeatedly introduce exactly the same failures in exactly the same way.
In the words of John Ousterhout,
"the only thing worse than a problem that happens all the time is a problem that doesn't happen all the time."
Therefore, our system must be \textit{deterministic}.

@@

Finally,
distributed systems are highly varied,
and as a result may require features or platform support not foreseen by our implementation.
Modularity in our design allows our framework to be easily extended,
not future-proofing it but allowing it to be future-proofed.
}

\section{Related Work}

{\fontsize{12}{15}\selectfont 
Though not a research paper,
Redstone was inspired by work done by the TigerBeetle team,
and their work in testing the TigerBeetle database.
This work heavily involves hastened testing of simulated distributed system faults.
However, the limitation of their work is that their simulator is compiled specifically for their software.
While this setup works for their well-abstracted code that they can freely recompile to embed the simulation,
there are many, many more distributed systems in the real world that are a poor match for this form of simulation.
As such, we wanted to try to take the idea they built their replicator on.
The basis of their simulator involves mocking all input and output:
their work includes a network simulator to force network faults and latencies,
and an in-memory storage simulator to force storage faults and latencies.
The simulator then speeds up the clock to make these I/O operations occur far more frequently than in production,
causing faults that may only occur once a year, or even more infrequently, to occur in a matter of days.
Such functionality would be highly valuable in testing nearly any production distributed system,
but, again, the context of TigerBeetle’s work is highly specific.
As such, we wanted to develop a framework that incorporates a number of the basic simulations TigerBeetle’s simulator includes
(namely, hastened I/O faults for network and in-memory storage),
but one that can be generally implemented on normal systems and run a much broader range of applications.
}

>>>>

%-------------------------------------------------------------------------------
\begin{abstract}
%-------------------------------------------------------------------------------
{\fontsize{12}{15}\selectfont 
In testing distributed systems,
confirming a system's tolerance of faults in disks and networks is not only useful but necessary.
Redstone, a modular deterministic simulation testing framework,
amplifies failures in various substrates underlying a distributed system
in order to confirm the system's ability to withstand these failures.
We intercept calls to the kernel for the disk and the network, as well as to clock functions,
introducing our own code.
Determinism allows reproduction of failure conditions,
allowing developers to confirm, having encountered and debugged a failure,
that their system will not fail again when confronted by identical conditions.
Our control over clock functions further allows us to ``accelerate" time,
increasing ability to test faster, and to emulate the effects of clock jitter.
Finally, because Redstone is inherently modular,
it is simple to extend and port to a wider variety of applications and platforms.

}
\end{abstract}

@@

``Consistently" is another key phrase here,
as a test must be replicable.
% just running the system a few times doesn't confirm that everything that can go wrong has gone wrong.
As such,
a good testing system must not only introduce failures,
but be able to repeatedly introduce exactly the same failures in exactly the same way.
In the words of John Ousterhout,
``the only thing worse than a problem that happens all the time is a problem that doesn't happen all the time."
Therefore, our system must be \textit{deterministic}.

@@

Finally,
distributed systems are highly varied,
and as a result may require features or platform support not foreseen by our implementation.
Modularity in our design allows our framework to be easily extended,
not future-proofing it but allowing it to be future-proofed.

}

\section{Related Work}
% Redstone was inspired by work done by the TigerBeetle team,
% and their work in testing the TigerBeetle database.
% However, the limitation of their work is that their simulator is compiled specifically for their software.

{\fontsize{12}{15}\selectfont 
Although their work is not a research paper,
the TigerBeetle team has provided inspiration to Redstone in their work developing a testing system for their database.
This work heavily involved hastened testing of simulated distributed system faults.
However, a significant limiting factor in their work as compared to ours is that the simulator is compiled specifically for the software being tested.
While this setup works for their well-abstracted code that they can freely recompile to embed the simulation,
there are many, many more distributed systems in the real world that this form of simulation suits poorly at best.

As such, we wanted to try to emulate the idea on which they built their replicator.
The basis of their simulator involves mocking all input and output:
their work includes a network simulator to force network faults and latencies,
and an in-memory storage simulator to force storage faults and latencies.
The simulator then speeds up the clock to make I/O operations occur far more frequently than in production,
causing faults that may only occur once a year, or even more infrequently, to occur in a matter of days.
Such functionality would be highly valuable in testing nearly any production distributed system.

Therefore,
we wanted to develop a framework that incorporates a number of features from the basic simulation methodologies
TigerBeetle’s simulator includes (namely, hastened I/O faults for network and in-memory storage),
but one that can be generally implemented on normal systems and run a much broader range of applications.

}
